Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-14 article.qmd
Spell-checker

For this last point,
IDEs that support `dataclass_transform` [@debontePEP681Data2021] can provide a tooltip with the expected signature (@fig-composition).
This requires the use of type annotations
which play a more significant role in static type checking,
as they can help to identify errors before running the code.
For instance, to parametrize the initial conditions of variables we have to use a `Constant`.
If we try to use a `Parameter`, which could be a time-dependent expression, it is flagged as a type error (@fig-ide).

@@

For the reaction networks,
our focus is on first-order differential equations
that describe the rate of change of species.
SimBio simplifies the definition of these network models by introducing `Species`,
which consists of a `poincare.Variable` and stoichiometry,
and `Reaction`,
a construct that converts reactants into products taking into account the stoichiometry (@fig-simbio).
Additionally, SimBio features `MassAction`, a subclass of `Reaction`,
which intuitively incorporates reactants into the rate law (@fig-simbio).

>>>>

For this last point,
IDEs that support `dataclass_transform` [@debontePEP681Data2021] can provide a tooltip with the expected signature (@fig-composition).
This requires the use of type annotations
which play a more significant role in static type checking,
as they can help to identify errors before running the code.
For instance, to parameterize the initial conditions of variables we have to use a `Constant`.
If we try to use a `Parameter`, which could be a time-dependent expression, it is flagged as a type error (@fig-ide).

@@

For the reaction networks,
our focus is on first-order differential equations
that describe the rate of change of species.
SimBio simplifies the definition of these network models by introducing `Species`,
which consists of a `poincare.Variable` and a stoichiometric number,
and `Reaction`,
a construct that converts reactants into products taking into account the stoichiometry (@fig-simbio).
Additionally, SimBio features `MassAction`, a subclass of `Reaction`,
which intuitively incorporates reactants into the rate law (@fig-simbio).
